%\documentclass[11pt]{amsart}
\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Review of the article\\
First-time observation of Timelike Compton Scattering}
\author{Valery Kubarovsky}
\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
\begin{itemize}

\item General remarks.\\
The target journal is PRL. \\
Manuscript  reported the first evermeasurement of Timelike Compton scattering. Boththe photon circular polarization asymmetry and Forward/Backward asymmetry were extracted. 
The comparison of the measured polarization asymmetry with model predictions points toward the interpretation of GPDs as universal functions. 
These results are  a significant achievement in the field.

The manuscript is well organized and clearly written. 
The technical quality and scientific rigor of the manuscript are very good and the main conclusion is well supported. 
The references to the literature are adequate. 
The title and abstract of the article are informative and clear. 

The theoretical introduction is understandable  for a nonspecialist.
The experimental setup and details of the data analysis are briefly described. 



\item Page 1, line 22\\
It is not clear what the authors want to tell. Do we have progress in Lattice QCD or not?\\
"In spite of the recent progress in Lattice QCD, QCD-based calculations cannot yet be performed to explain the properties of nucleons in terms of their constituents."
\item Page 1, line 23\\
Language: ...in Lattice QCD, QCD-based...
\item Page 1, line 31\\
Language: The whole sentence starting with\\
 They describe..., they give....,and they are
\item Page 1, line 65\\
   $t = (p-p')^2$
\item Page 1, line 70\\
Insert  noindent 
\item Line 84, 169, 180, 226, 227, 245302, 307, 321\\
Figure 2 $\to$ Fig.~2 etc.
\item Page 2, line 136\\
High Threshold
\item Page 2, line 139\\
minimimum $\to$ minimum
\item Page 2, line 164\\
Remove brackets in $\cos\theta_X$\\
$Q^2=2E_bE_X(1-\cos\theta_X)$
\item Page 2\\
Eq.6 is confusing. $E_X$ and $\theta_X$ are unknown.
\item Fig. 3. Change red color to black. \\
Also add above 1.5 GeV and below $J/\psi$ mass
\item Page 3, line 185\\
$e^+e^-$, "-" has to be in upper script
\item Page 4, line 253-254\\
The error bars of the average kinematics 
E= $7.29\pm1.55$ GeV; $M = 1.8\pm0.26$ GeV are not discussed in the letter.
\item Page 4, line 274\\
tends
\item Page 4, line 318\\
underestimates
\item Page 5, line 340\\
Jlab
\item Page 5, line 370\\
Move reference "*chatagnon@ipno.in2p3.fr"  to Page 1.
\item Page 5, line 376\\
Move [5] in front of [4]
\item Page 5, line 383\\
Remove 0711.4805
\item Page 6 line 430\\
Remove 1704.07330
\end{itemize}


\end{document}
